### 2018-05-15 msc_diploma_cubesat_galgoczi.tex
ii

@@

\section{Results of the simulation}
\subsection{Comparison of the results of the simulation with experiments}
\subsubsection{Calibration of the position dependence}

@@

\subsection{X-ray fluorescence}
Histogram without fluorescence, turned out in LXeEMPhysics line 140-159

@@

In order to include the resonances in the cross section of the hadron-hadron interactions, additional physics models are needed to be included in the simulation. The signal induced by these resonances might affect the measurement of the protons.
\subsection{Optimalization of the scintillator detectors}

@@

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/grb_spectra.png}
\caption{The band function of GRB 9900123 $\cite{grb_spectra}$}
\end{figure}

@@

\section{Results of the simulation}

\subsection{Comparison of the results of the simulation with experiments}

\subsubsection{X-ray fluorescence}

Histogram without fluorescence, turned out in LXeEMPhysics line 140-159

\subsubsection{Calibration of the position dependence}

@@

\begin{figure}
\includegraphics[width=150.0mm]{images/calibration_photon_yield.png}[H!]
\caption{The satellite radiated by a pencil beam of 10.000 $\gamma$ particles. The scattered $\gamma$s induce signal in the scintillator}
\end{figure}

The energy bins had to be scaled up by a factor of 2.4 to match the experimental results. The amplitude had to be scaled up by a factor of 26.2.

@@

In order to include the resonances in the cross section of the hadron-hadron interactions, additional physics models are needed to be included in the simulation. The signal induced by these resonances might affect the measurement of the protons.

Protons
'Apogee: 500.0 km'
'Perigee: 500.0 km'
'Inclination: 89.0 deg'

Electrons
'Trapped electron model: AE-8 MIN'
%'Energy','MeV','Energy'
%'IFlux','cm^-2 s^-1','Integral Flux'
%'DFlux','cm^-2 s^-1 MeV^-1','Differential Flux'

@@

\bibitem{grb_spectra} Gamma-Ray Bursts and Fast Transients
Multi-wavelength Observations and Multi-messenger Signals,\\
R. Willingale, P. Mészáros
%https://link.springer.com/content/pdf/10.1007/s11214-017-0366-4.pdf
